---
title: "PAITC Systematic Review Results"
format: pdf
---

```{r config knitr, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(error = FALSE)
knitr::opts_chunk$set(message = FALSE)

knitr::opts_chunk$set(fig.width = 12)
knitr::opts_chunk$set(fig.height = 8)
```


```{r}
library(readr)
library(stringr)
library(dplyr)
library(tidyr)
library(tibble)
library(purrr)
library(lubridate)
library(ggthemr)
library(arsenal)
library(flextable)

source("R_snippets.R")
ggthemr::ggthemr("fresh")
```


```{r}
all_articles_info <- read_csv("data/articles_selection/all_articles_info.csv", col_types = cols(.default = "c"))
all_articles_id <- read_csv("data/articles_selection/articles_id.csv", col_types = cols(.default = "c"))
# extraction_list <- read_csv("data/articles_selection/included_articles_after_review.csv", col_types = cols(.default = "c)))
flow_chart_df <- read_csv("data/to_use_for_stats/flow_chart.csv", col_types = cols(included = "l",
                                                                                   full_article = "l",
                                                                                   third = "l",
                                                                                   during_extraction = "l",
                                                                                   .default = "c"))
results_df <- read_tsv("data/to_use_for_stats/long_results_final.tsv", col_types = cols(.default = "c"))
ttt_mapped <- read_tsv("data/to_use_for_stats/decision_atc_mapped.tsv", col_types = cols(.default = "c", car_t_cells = "l"))
conditions_mapped <- read_tsv("data/to_use_for_stats/decision_icd_mapped.tsv", col_types = cols(.default = "c"))
```


```{r}
source("questions_sections.R")
methodology_questions <- questions_sections$methodology %>% unname()
```


```{r}
# selection articles ---------------------------------------------------------
all_articles_id <- all_articles_id %>%
  mutate(DOI = tolower(DOI)) %>%
  rename(doi = DOI)
included_articles <- filter(flow_chart_df, included)

results_df <- left_join(results_df, all_articles_id[, c("doi", "PMID")], by = "doi")

stopifnot(identical(
  unique(included_articles$PMID)[order(unique(included_articles$PMID))],
  unique(results_df$PMID)[order(unique(results_df$PMID))]
))

included_articles_info <- semi_join(all_articles_info, included_articles, by = "PMID")
```


```{r Creating section data frames}
general_information_df <- results_df[results_df$section == "general_information",]
individual_study_df <- results_df[results_df$section == "study_information",]
paitc_results <- results_df[results_df$section %in% c("methodology", "results"), ]
```

```{r Wide methodo}
wide_methodo <- paitc_results %>% 
  filter(section == "methodology") %>% 
  pivot_wider(id_cols = c(doi, PMID, n_itc), names_from = questions, values_from = answer)
```


```{r Wide results}
wide_results <- paitc_results %>% 
  filter(section == "results") %>% 
  pivot_wider(id_cols = c(doi, PMID, n_itc), names_from = questions, values_from = answer)
```

```{r Wide methodo results}
wide_methodo_results <- paitc_results %>% 
  pivot_wider(id_cols = c(doi, n_itc), names_from = questions, values_from = answer)
```


# Articles general Information

```{r}
general_information_df <- general_information_df %>% 
  select(-n_itc, -study_number, -section, -PMID) %>% 
  select(answer, everything())
```


## Journals

```{r Publication journals, fig.height=18}
#TODO: rajouter IF
## Authors specific affiliations would need to be parsed and retrieved through pubv1_info.txt --> regex looking at ". " preceded by a ", " or "^"
included_articles_info %>%
  mutate("journal_title" = JT,
         "journal_title_short" = TA) %>%
  group_by(journal_title_short) %>%
  summarise(count = n()) %>%
  arrange(desc(count)) %>%
  ggplot(aes(x = reorder(journal_title_short, count), y = count, label = count)) +
  geom_bar(stat = "identity") +
  geom_label() + 
  theme(axis.text.y = element_text(size = 12)) +
  scale_x_discrete() +
  coord_flip() +
  labs(title = "Publication journals",
       x = "Journals",
       y = "Articles count")
```


```{r Publication date}
## Publication dates
publication_date_df <- included_articles_info %>%
  select(EDAT) %>%
  mutate(publication_date = as_date(EDAT, format = "%Y/%m/%d %H:%M"),
         publication_year = year(publication_date),
         publication_date_q = lubridate::quarter(publication_date, with_year = TRUE),
         publication_date_s = lubridate::semester(publication_date, with_year = TRUE),
         publication_date_s = ifelse(round(publication_date_s %% 0.2, 1) == 0.1,
                                      trunc(publication_date_s),
                                      trunc(publication_date_s) + 0.5))


publication_date_df %>%
  filter(publication_year < 2022) %>%
  group_by(publication_year) %>%
  summarise(count = n()) %>%
  ggplot(aes(x = publication_year, y = count)) +
  geom_point() +
  geom_line() +
  geom_text(aes(label = count), nudge_y = 2.5, nudge_x = -0.05) +
  scale_x_continuous(breaks = 2010:2022) +
  labs(title = "MAIC/STC implementation: publications by years",
       x = "Year",
       y = "Publication counts")
```
```{r Intervals between articles received and accepted}
publication_dates_df <- included_articles_info %>% mutate(
  received_date = str_extract(PHST, "[^\\].]+(?=\\[received\\])") %>% str_trim() %>% as_datetime(format = "%Y/%m/%d %H:%M"),
  accepted_date = str_extract(PHST, "[^\\].]+(?=\\[accepted\\])") %>% str_trim() %>% as_datetime(format = "%Y/%m/%d %H:%M"),
  pubmed_date = str_extract(PHST, "[^\\].]+(?=\\[pubmed\\])") %>% str_trim() %>% as_datetime(format = "%Y/%m/%d %H:%M"), 
  time_acceptation = accepted_date - received_date, 
  time_publication_pubmed = pubmed_date - received_date
) %>% 
  select(PHST, received_date, accepted_date, time_acceptation, time_publication_pubmed, pubmed_date, PMID, PT, TA, PL, JT)

publication_dates_df %>% 
  pivot_longer(cols = c(time_acceptation, time_publication_pubmed), names_to = "time_type", values_to = "time") %>% 
  mutate(time = time/30.5) %>% 
  ggplot(aes(x = time)) + 
  facet_wrap(~ time_type) +
  geom_histogram() + 
  labs(x = "Time in months", "publication count", 
       title = "Time between submission and acceptation")
```
## Authors' affiliations

```{r Authors affiliations}
authors_affiliation_df <- general_information_df %>% 
  filter(questions == "Positions of study investigators (for any authors of the article, any that applies)") %>%
  # Manually correcting variation introduced during the review process 
  mutate(answer = if_else(answer == "Academic, Private Data Analysis Company, Pharmaceutical Industry",
                         "Academic, Pharmaceutical Industry, Private Data Analysis Company",
                         answer)) %>%
  select(doi, answer) %>% 
  mutate(positions = str_split(answer, ", ")) %>% 
  unnest(positions)
```


```{r }
authors_affiliation_df %>% 
  distinct(doi, answer) %>% 
  count(answer) %>% {
  ggplot(., aes(x = answer, y = n)) +
  geom_bar(stat = "identity") +
  geom_label(aes(label = n), 
             position = position_stack(vjust = 0.5)) + 
  coord_flip() + 
  scale_x_discrete(limits = rev(.$answer)) +
  labs(x = NULL, y = "Articles count", title = "Authors' positions") +
  theme(axis.text.y = element_text(size = 8))
}
```


```{r}
authors_affiliation_df %>% 
  group_by(positions) %>% 
  summarise(counts = n()) %>% 
  ggplot(aes(x = positions, y = counts)) +
  geom_bar(stat = "identity") +
  geom_label(aes(y = 150, label = counts),
             position = position_stack(vjust = 0.5),
             color = "black",
             show.legend = FALSE) + 
  labs(title = "Authors' positions",
       subtitle = "At least one author affiliated with: ", 
       y = "Articles count", 
       x = "Positions")
```


```{r }
authors_affiliation_df %>% 
  mutate(counter = TRUE) %>% 
  pivot_wider(names_from = positions, values_from = counter, values_fill = FALSE) %>% 
  mutate(collaboration = Academic & `Pharmaceutical Industry`) %>% 
  count(collaboration) %>% 
  ggplot(aes(x = collaboration, y = n)) + 
  geom_bar(stat = "identity") + 
  geom_label(aes(label = n, y = 30)) +
  scale_x_discrete(labels = c(`FALSE` = "No collaboration", `TRUE` = "Collaboration")) +
  labs(x = NULL, 
       y = "Articles count", 
       title = "Academics/Pharmaceutical Collaborations")
```

### First and last authors positions

```{r}
general_information_df %>% 
  mutate(answer = ifelse(tolower(answer) %in% c("usa", "uk"),
                         str_to_upper(answer),
                         str_to_title(answer))) %>% 
  filter(questions %in% c("Countries of first author affiliations", "Countries of last author affiliations")) %>% 
  count(questions, answer) %>%
  ggplot(aes(x = reorder(answer, n), y = n)) + 
  geom_bar(stat = "identity") + 
  facet_grid(" ~ questions") + 
  coord_flip() + 
  labs(title = "Countries", 
       x = NULL, 
       y = "Article count")
  
```

## Methodology departments


```{r}
general_information_df %>% 
  filter(questions == "At least one author affiliated with a department of Biostatistics, Epidemiology, Public Health, Pharmacoepidemiology, or a Clinical Research unit, or private data analysis company") %>% 
  count(answer) %>% 
  ggplot(aes(x = answer, y = n, label = n)) +
  geom_bar(stat = "identity") +
  geom_label() +
  labs(x = "Affiliation with a methodology department/data-analysis company", 
       title = "Involvement of a Methodology department/data-analysis company", 
       y = "Count")
```

## Ties with pharmaceutical industry 



```{r}
ties_w_pharma_df <- general_information_df %>% 
  filter(questions %in% c("Positions of study investigators (for any authors of the article, any that applies)", 
                          "Mentioned sources of funding")) %>% 
  pivot_wider(id_cols = doi, names_from = questions, values_from = answer) %>% 
  mutate(ties_pharma = ifelse(grepl("Pharmaceutical", `Positions of study investigators (for any authors of the article, any that applies)`) | grepl("Pharmaceutical Industry", `Mentioned sources of funding`), TRUE, FALSE))

```

```{r}
general_information_df %>% 
  filter(questions == "Ties with pharmaceutical industry mentionned in competing interest/conflict of interest/disclaimer, or any equivalent section in the article") %>% 
  count(answer) %>% 
  ggplot(aes(x = answer, y = n, label = n)) +
  geom_bar(stat = "identity") +
  geom_label() +
  coord_flip() + 
  labs(x = NULL,
       title = "Ties with pharma in COI section", 
       y = "Count")
```


## Fundings

```{r}
general_information_df %>% 
  filter(questions == "Mentioned sources of funding") %>% 
  count(answer) %>% 
  ggplot(aes(x = answer, y = n, label = n)) +
  geom_bar(stat = "identity") +
  geom_label() +
  coord_flip() + 
  labs(x = NULL,
       title = "Mentioned of source of fundings", 
       y = "Count")
```


## Investigated medical conditions

```{r fig.width=12}
conditions_df <- general_information_df %>% 
  filter(questions == "Medical Condition of Interest Name") %>% 
  left_join(conditions_mapped, by = c("answer" = "condition_name"))
# conditions_df
stopifnot(!any(is.na(conditions_df$`concept_name_ICD10 Chapter`)))
```


```{r fig.width=12, fig.height=10}
conditions_df %>% 
  count(`concept_name_ICD10 Hierarchy`, `concept_code_ICD10 Hierarchy`) %>% 
  mutate(across(where(is.character), as.factor)) %>% 
  ggplot(aes(x = reorder(`concept_name_ICD10 Hierarchy`, as.numeric(`concept_code_ICD10 Hierarchy`)),
             y = n, 
             label = n)
  ) + 
  geom_bar(stat = "identity") +
  geom_label() + 
  coord_flip() +
  scale_y_discrete() + 
  labs(x = NULL, 
       y = "Articles count", 
       title = "Investigated Condition", 
       subtitle = "By ICD-10 Subchapter")

```


```{r fig.width=12}
conditions_df %>% 
  count(`concept_name_ICD10 Chapter`, `concept_code_ICD10 Chapter`) %>% 
  mutate(across(where(is.character), as.factor)) %>% 
  ggplot(aes(x = reorder(`concept_name_ICD10 Chapter`, as.numeric(`concept_code_ICD10 Chapter`)),
             y = n, 
             label = n)
  ) + 
  geom_bar(stat = "identity") +
  geom_label() + 
  coord_flip() + 
  labs(x = NULL, 
       y = "Articles count", 
       title = "Investigated condition", 
       subtitle = "By ICD-10 Chapter")

```

# Results


```{r data management to determine IPD/nonIPD treatments}
ttt_ipd_df <- paitc_results %>% 
  select(doi, section, n_itc, questions, answer) %>% 
  filter(str_detect(questions,
                    pattern = c("(Treatment name)|(Study 'number\\(s\\)' for treatment)"))) %>% 
  separate(questions, into = c("questions", "treatment number"), 
           sep = "\\s(?=\\d$)"
  ) %>% 
  pivot_wider(names_from = questions, 
              values_from = answer) %>% 
  mutate(`Study 'number(s)' for treatment` = str_split(`Study 'number(s)' for treatment`, ";")) %>% 
  unnest_longer(`Study 'number(s)' for treatment`) %>% 
  left_join(individual_study_df %>% 
              filter(questions == "Patient-level data used") %>% 
              pivot_wider(names_from = questions, values_from = answer) %>% 
              rename(IPD = `Patient-level data used`) %>% 
              mutate(IPD = stringr::str_to_title(IPD)) %>% 
              select(doi, study_number, IPD), 
            by = c("doi" = "doi", "Study 'number(s)' for treatment" = "study_number")
  )

stopifnot(
  "Some combinations of doi-n_itc-treatment are assigned both IPD and non IPD" = nrow(distinct(ttt_ipd_df, doi, `treatment number`, n_itc, `Treatment name`, IPD)) == nrow(distinct(ttt_ipd_df, doi, n_itc, IPD))
)

```


### Treatments

```{r Finding out similar comparisons}

ipd_non_ipd_df <- ttt_ipd_df %>%
  distinct(doi, `Treatment name`, n_itc, IPD) %>% 
  left_join(distinct(ttt_mapped[, c("decision", "first", "second", "third", "car_t_cells")]),
            by = c("Treatment name" = "decision")) %>% 
  pivot_wider(id_cols = c(doi, n_itc), names_from = c("IPD"), values_from = "first") %>% 
  left_join(conditions_df[, c("doi", "concept_name_ICD10 Hierarchy")], by = "doi") %>% 
  distinct(doi, Yes, No, `concept_name_ICD10 Hierarchy`) %>% 
  rename(condition = `concept_name_ICD10 Hierarchy`)


inverted_ipd <- ipd_non_ipd_df %>% 
  mutate(Yes_temp = No, No = Yes, Yes = Yes_temp) %>% 
  select(doi_inv = doi, Yes, No, condition)
same_comparisons <- inverted_ipd %>%
  inner_join(ipd_non_ipd_df,
             by = c("Yes", "No", "condition")) %>% 
  select(doi, doi_inv, everything()) %>% 
  filter(doi != doi_inv) %>% 
  rowwise() %>% 
  mutate(doi_pair = list(sort(c(doi, doi_inv)))) %>%
  ungroup() %>% 
  distinct(doi_pair, Yes, No, condition) %>% 
  unnest_wider(doi_pair, names_sep = "_")

```


```{r, fig.height = 18}

ttt_ipd_df %>% 
  mutate(IPD = tolower(IPD) %>% factor(levels = c("yes", "no"))) %>% 
  #TODO: fix the NA issue
  filter(!is.na(IPD)) %>% 
  distinct(doi, n_itc, `treatment number`, `Treatment name`, IPD) %>% 
  left_join(distinct(ttt_mapped[, c("decision", "first", "second", "third", "car_t_cells")]),
            by = c("Treatment name" = "decision")) %>%
  group_by(IPD) %>% 
  count(first) %>% 
  ggplot(aes(x = reorder(first, n), y = n, label = n)) +
  geom_bar(stat = "identity") +
  geom_label() +
  coord_flip() +
  facet_wrap(c("IPD"), labeller = labeller("IPD" = c("no" = "Non IPD", "yes" = "IPD"))) +
  labs(title = "Treatments compared", 
       subtitle = "ATC classification level 2") +
  theme(axis.text = element_text(size = 16), 
        strip.text = element_text(size = 18), 
        plot.title = element_text(size = 22), 
        plot.subtitle = element_text(size = 20))
```


## Individual studies 

```{r, results='asis'}
individual_studies_questions <- c(
  "Patient-level data used", 
  "Clinical Trial", 
  "Country where the clinical trial/observational study was conducted (international if more than one)",
  "Phase of the clinical trial (clinical trial only)", 
  "Number of treatment arms (clinical trial only)"
)

individual_study_df %>% 
  mutate(answer = str_to_title(answer)) %>% 
  #TODO: fix this "Xx'
  filter(answer != "Xx") %>%
  pivot_wider(names_from = questions, values_from = answer) %>% 
  select(all_of(individual_studies_questions)) %>% 
  tableby(`Patient-level data used` ~ ., data = .) %>% 
  summary()
```

### Methodology statistics per article

```{r, results='asis'}
# results at the article level: eg "at least one ... per article"
wide_methodo_results %>% 
  group_by(doi) %>% 
  # to fix the few cases where max(n_itc) isn't the number of comparisons performed
  summarise(count_comparisons = n(), 
            at_least_one_maic = any(paitc_type == "MAIC"), 
            at_least_one_stc = any(paitc_type == "STC"),
            at_least_other_paitc = any(!paitc_type %in% c("MAIC", "STC")), 
            ) %>% 
  select(-doi) %>% 
  `labels<-`(c(
    "count_comparisons"    = "PAITC count (per article)",
    "at_least_one_maic"    = "At least one MAIC in the article", 
    "at_least_one_stc"     = "At least one STC in the article", 
    "at_least_other_paitc" = "At least one other PAITC")) %>% 
  tableby( ~ ., data = .) %>% 
  summary() 
```

## Methodology per comparisons

```{r}

# Only binary variables
list_questions_methodo <- c(
  "Type of population-adjusted indirect comparisons performed" = "paitc_type",
  "Anchored comparison?" = "anchored_yn",
  "Form of the indirect comparison" = "paitc_form",
  "Definition of a single primary outcome for the indirect comparison" = "primary_outcome_yn",
  # "Primary Outcome Name (first one mentioned in the text of the results part if no primary outcome defined)" = "Primary Outcome Name (first one mentioned in the text of the results part if no primary outcome defined)", #TODO --> non UTF8 characther somewhere, to be fixed
  "Primary outcome: variable type" = "primary_outcome_type",
  # "Justification for selecting variables to be included in the adjustment model (in the main text)" = "Justification for selecting variables to be included in the adjustment model (in the main text)",
  "Inclusion of prognostic factors in the adjustment/matching model" = "prognostic_factors_yn",
  "Inclusion of treatment-effect modifiers in the adjustment/matching model" = "ttt_effect_modifiers_yn",
  "Mention of the MAIC weights estimation model / STC adjustment model details in the main text **or supplemental materials** (ie matching on first moment, second moment, including interaction term, etc)" = "weights_model_yn",
  "Discussion of the choice of the scale for the outcome in the main text (ie natural outcome scale vs transformed outcome scale)" = "scale_choice_yn"
)
```


```{r, results='asis'}
wide_methodo %>%
  select(all_of(list_questions_methodo)) %>% 
  # Apparently select rename the columns using the names of list_questions_methodo ...
  tableby(list(`Type of population-adjusted indirect comparisons performed`, `Anchored comparison?`) ~ ., data = .) %>% 
  summary()
```

### Variables selection justification


```{r DM Variables selection, results='asis'}
variables_selection <- wide_methodo %>% 
  select(doi, n_itc, variables_justification) %>% 
  # because the complete item for this one is "Nothing mentioned, not reported", thus simplyfying it
  mutate(variables_justification = variables_justification %>% 
           str_split(",") %>% 
           map(~ str_trim(.x)) %>% 
           map(~ .x[.x != "not reported"])) %>%
  mutate(no_justification = sapply(variables_justification, function(x) any(x == "Nothing mentioned")), 
         incorrect_or_no_justification = sapply(variables_justification,
                                          function(x) all(x %in% c(
                                            "Nothing mentioned",
                                            "Statistical imbalanced between treatment groups (independently of the status of prognostic/effect modifier)",
                                            "Status of prognostic factor/treatment effect modified assessed in the IPD dataset"
                                          )))
  )


# Handling of list like columns 
# (ie multiple choices questions : to be concatenated with merge(tab1, tab2, all = TRUE))
# update: this only works if the total are identical, which is not the case here
# solution is to merge downstream with flextable probably, or not merging at all
# Plot using 'group' see https://jennybc.github.io/purrr-tutorial/ls13_list-columns.html
justif <- variables_selection %>% 
  unnest_longer(col = variables_justification) %>% 
  tableby(~ variables_justification, data = .)

# Variables selection
justif_binary <- variables_selection %>% 
  tableby(~ no_justification + incorrect_or_no_justification, data = .) 

justif_binary %>% 
  summary(title = "Covariates selection justification")
# merge(justif, justif_binary, all = FALSE)

#TODO: stratifying by anchored/unanchored, and STC/MAIC as outcome

```

### Sample sizes

```{r}
wide_sample_size_df <- wide_results %>% 
  left_join(distinct(wide_methodo, doi, n_itc, `anchored_yn`, paitc_type)) %>% 
  select(doi, n_itc, anchored_yn, paitc_type, contains(c("n_ipd", "n_nonipd", "ess"))) %>%
  mutate(across(contains(c("n_ipd", "n_nonipd", "ess")), as.integer)) %>% 
  mutate(
    n_ipd_total = case_when(
      !is.na(n_ipd_total) ~ n_ipd_total,
      anchored_yn == "No" ~ n_ipd_ttt, 
      anchored_yn == "Yes" ~ n_ipd_ttt + n_ipd_anchor, 
      TRUE ~ NA_integer_),
    n_nonipd_total = case_when(
      !is.na(n_nonipd_total) ~ n_nonipd_total,
      anchored_yn == "No" ~ n_nonipd_ttt, 
      anchored_yn == "Yes" ~ n_nonipd_ttt + n_ipd_anchor, 
      TRUE ~ NA_integer_),
    ess_total = case_when(
      !is.na(ess_total) ~ ess_total,
      anchored_yn == "No" ~ ess_ttt,
      anchored_yn == "Yes" ~ ess_ttt + ess_anchor,
      TRUE ~ NA_integer_)
  ) %>% 
  mutate(difference_ess_ttt = n_ipd_ttt - ess_ttt,
         difference_ess_anchor = n_ipd_anchor - ess_anchor, 
         difference_ess_total = n_ipd_total - ess_total, 
         rapport_ess_ttt = ess_ttt / n_ipd_ttt,
         rapport_ess_anchor = ess_anchor / n_ipd_anchor,
         rapport_ess_total = ess_total / n_ipd_total)

long_sample_size_df <- wide_sample_size_df %>% 
  select(-doi, -n_itc) %>% 
  pivot_longer(cols = !all_of(c("anchored_yn", "paitc_type"))) %>% 
  mutate(ipd_yn = case_when(
    grepl("total", name) ~ "Total",
    grepl("_ipd_", name) | grepl("ess_", name) ~ "IPD", 
    grepl("_nonipd_", name) ~ "Non IPD",
    TRUE ~ NA_character_
  ),
  sample_size_type = case_when(
    grepl("difference", name) ~ "Difference",
    grepl("rapport", name) ~ "Rapport", 
    grepl("ess", name) ~ "ESS",
    TRUE ~ "Original")
  )
```

```{r, results='asis'}
wide_sample_size_df %>% 
  mutate(
    anchored_yn = ifelse(anchored_yn == "Yes", "Anchored", "Unanchored"),
    n_ipd_yn = ifelse(is.na(n_ipd_total) & is.na(n_ipd_ttt), "No", "Yes"), 
    n_nonipd_yn = ifelse(is.na(n_nonipd_total) & is.na(n_nonipd_ttt), "No", "Yes"), 
    ess_yn = ifelse(is.na(ess_ttt) & is.na(ess_total), "No", "Yes"), 
) %>% 
  tableby(list(anchored_yn, paitc_type) ~ n_ipd_yn + n_nonipd_yn + ess_yn, data = .) %>% 
  summary()
```

```{r Sample size reduction, fig.width = 14}

sample_size_labels <- c(
  Rapport = "Rapport ESS/Original",
  Difference = "Difference Original - ESS", 
  Original = "Original Sample Size", 
  ESS = "ESS"
)

long_sample_size_df %>% 
  filter(paitc_type %in% c("MAIC"), 
         ipd_yn == "Total") %>%
  mutate(sample_size_type = factor(sample_size_type, levels = c("Original", "ESS", "Difference", "Rapport"))) %>% 
  # filter(ipd_yn == "Total") %>% 
  ggplot(aes(x = 1, y = value)) +
  geom_violin() + 
  geom_jitter(width = 0.2) + 
  facet_wrap(~ sample_size_type,
             scales = "free",
             ncol = 4, 
             labeller = labeller( sample_size_type = sample_size_labels)) +
  theme(legend.position = "bottom", legend.direction = "horizontal", axis.ticks =  element_blank()) +
  labs(title = "Sample Size Reduction in MAIC", 
       y = "Sample Size", 
       x = NULL)

```



### Outcomes 


```{r, results='asis'}

funded_pharma <- general_information_df %>% select(doi, )
wide_methodo_results  %>% 
  mutate(across(.cols = c(outcome_short_name, primary_outcome_name), 
                .fns = stringr::str_to_title)
  ) %>% 
  add_count(primary_outcome_name, name = "primary_outcome_name_n") %>% 
  mutate(primary_outcome_name = forcats::fct_reorder(primary_outcome_name,
                                                     primary_outcome_name_n, 
                                                     .desc = TRUE)) %>% 
 # TODO : fix missing outcome name 
  tableby( primary_outcome_yn ~  primary_outcome_type + outcome_short_name,
           data = .) %>% 
  summary()
```

### Treatment effect estimates

```{r}
# renaming_contrast <- c(
#   "Incidence Rate Ratio" = "Rates: OR/RR/means ratio", 
#   "Rate ratio" = "Rates: OR/RR/means ratio", 
#   "OR" = "Rates: OR/RR/means ratio", 
#   "RR" = "Rates: OR/RR/means ratio", 
#   "Means Ratio" = "Rates: OR/RR/means ratio", 
#   "Means difference" = "Means/medians difference", 
#   "Median difference" = "Means/medians difference", 
#   "RMST difference at 12 months" = "Means/medians difference",
#   "Risk difference" = "Risk/Rate difference", 
#   "Rate difference" = "Risk/Rate difference", 
#   "HR" = "Hazard Ratio", 
#   "Proportion difference" = "Proportion difference",
#   "Proportions difference" = "Proportion difference"
# )

renaming_contrast <- c(
  "Incidence Rate Ratio" = "Rates/ratio", 
  "Rate ratio" = "Rates/ratio", 
  "OR" = "Rates/ratio", 
  "RR" = "Rates/ratio", 
  "Means Ratio" = "Rates/ratio", 
  "Means difference" = "Difference", 
  "Median difference" = "Difference", 
  "RMST difference at 12 months" = "Difference",
  "Risk difference" = "Difference", 
  "Rate difference" = "Difference", 
  "HR" = "Rates/ratio", 
  "Proportion difference" = "Difference",
  "Proportions difference" = "Difference"
)

wide_results_outcome <- wide_methodo_results %>% 
   mutate(contrast = replace_in_vec(contrast, renaming_contrast)) %>% 
  select(doi, n_itc, contrast, effect_direction, unadjusted_lb_ci, unadjusted_ub_ci,
         adjusted_lb_ci, adjusted_ub_ci, unadjusted_significant, adjusted_significant, 
         effect_cutoff, unadjusted_num_pval, adjusted_num_pval, unadjusted_effect, 
         adjusted_effect, direction_benefit, outcome_short_name) %>% 
  pivot_longer(names_pattern = "((?:un)?adjusted)(_)(.*)", 
               cols = !c(doi, n_itc, contrast, effect_direction, direction_benefit, outcome_short_name, effect_cutoff), 
               names_to = c("adjustment", NA, "indicator"), 
               values_to = "values") %>%
  pivot_wider(id_cols = c(doi, n_itc, contrast, effect_direction, adjustment, direction_benefit, outcome_short_name, effect_cutoff), 
              names_from = indicator, 
              values_from = values) %>% 
  mutate(across(c(lb_ci, ub_ci, num_pval, effect, effect_cutoff), as.numeric)) 


# Standarsize what is beneficial for IPD
# stopifnot(all(!is.na(wide_results_outcome$direction_benefit)))
# stopifnot(all(!is.na(wide_results_outcome$effect)))
# table(is.na(wide_results_outcome$effect), useNA = "always")
# table(is.na(wide_results_outcome$effect_cutoff), useNA = "always")
# wide_results_outcome %>% filter(!is.na(effect) & is.na(effect_cutoff)) %>% View()

left_side_outcome <- wide_results_outcome %>% 
  filter(effect_direction == "Numerator if ratio, or left side if difference")

right_side_outcome <- wide_results_outcome %>% 
  filter(effect_direction == "Denominator if ratio, or rightside if difference") %>% 
  mutate(across(c(lb_ci, ub_ci, effect),
                .fns = function(x) {
                  ifelse(effect_cutoff == 0, -x, ifelse(effect_cutoff == 1, 1/x, NA))
                })
  ) %>% 
  mutate(lb_ci_temp = ub_ci, 
         ub_ci = lb_ci, 
         lb_ci = lb_ci_temp, 
         lb_ci_temp = NULL)

wide_results_outcome <- bind_rows(left_side_outcome, right_side_outcome) %>%
  select(-effect_direction) %>%
# Creating binary variable distinguishing estimates beneficial for IPD:
  mutate(benefit_ipd = case_when(
    direction_benefit == "inferior" & effect <= effect_cutoff ~ TRUE,
    direction_benefit == "superior" & effect >= effect_cutoff ~ TRUE,
    !is.na(effect) ~ FALSE,
    TRUE ~ NA)
  )
```


```{r, eval = FALSE}
wide_results_outcome %>%
  #TODO: see what is the best to do with contrast == NA
  filter(!is.na(contrast)) %>%
  ggplot(aes(x = adjustment, y = effect, color = significant)) +
  geom_jitter(width = 0.1) +
  geom_hline(aes(yintercept = effect_cutoff), linetype = "dashed", color = "black") +
  facet_wrap(~ contrast, scales = "free_y") +
  scale_y_continuous(trans = "log10") +
  labs(title = "Treatment contrast effects: point estimates",
       subtitle = "IPD is numerator for rates/ratio, left side differences",
       y = "Estimate",
       x = NULL
  )


```

```{r}
wide_results_outcome %>% 
  left_join(ties_w_pharma_df, by = "doi") %>% 
  filter(adjustment == "adjusted", significant == "TRUE", ties_pharma, !benefit_ipd) %>% 
  View()
```


## Results benefit IPD
```{r, results='asis'}
wide_results_outcome %>% 
  left_join(ties_w_pharma_df, by = "doi") %>% 
  tableby(benefit_ipd ~ significant, strata = adjustment, data = .) %>% 
  summary(title = "Treatment point estimate benefits IPD") 
```

```{r, fig.width=14, fig.height=12}
outcomes_df <- wide_results_outcome %>% 
  select(doi, n_itc, adjustment, contrast, direction_benefit, outcome_short_name, effect_cutoff, significant, benefit_ipd, effect) %>% 
  filter(!is.na(effect)) %>% 
  # Creating a variable where a beneficial effect for IPD is always inferior to threshold
  mutate(effect_benefit = case_when(
    direction_benefit == "superior" & effect_cutoff == 0 ~ -effect, 
    direction_benefit == "superior" & effect_cutoff == 1 ~ 1/effect,
    TRUE ~ effect,
  ), 
  significant_char = case_when(
    significant == "TRUE" ~ "Yes",
    significant == "FALSE" ~ "No", 
    is.na(significant) ~ "Unknown")) 

num_comparison_df <- outcomes_df %>% 
  distinct(n_itc, doi, contrast) %>% 
  group_by(contrast) %>% 
  mutate(num_comparison = 1:n()) %>% 
  ungroup()

outcomes_df <- outcomes_df %>% 
  left_join(num_comparison_df)
```


```{r, fig.width=14, fig.height=12}
labelling_data <- data.frame(
  contrast = unique(outcomes_df$contrast), 
  left_side = "Favors IPD", 
  right_side = "Favors non-IPD"
) %>%
  left_join(distinct(outcomes_df, contrast, effect_cutoff)) %>% 
  left_join(summarise(group_by(outcomes_df[, c("contrast", "effect", "num_comparison")], contrast),
                      left_x = min(effect), 
                      right_x = max(effect), 
                      max_num_comparison = max(num_comparison)))
```


```{r, fig.width=14, fig.height=16}
outcomes_df %>% 
  ggplot(aes(x = effect_benefit, y = num_comparison, color = significant_char, shape = adjustment)) + 
  geom_point(size = 3) +
  geom_vline(aes(xintercept = effect_cutoff), linetype = "dashed", color = "black") +
  # geom_blank(aes(y = max_num_comparison * 1.1, x = 3), inherit.aes = FALSE, data = labelling_data) +
  scale_color_manual(values = c("Yes" = "#cc0000", "No" = "#000000", "Unknown" = "#D9D9D9")) +
  facet_wrap(~ contrast, scales = "free") + 
  labs(title = "PAITC treatment effects point estimates", 
       subtitle = "Left side of vertical dashed line favors IPD", 
       color = "5% significance level", 
       shape = "Adjustment",
       x = "Treatment effect point estimate", 
       y = NULL) +
  theme(legend.position = "bottom",
        text = element_text(size = 14),
        axis.text.y = element_blank(),
        axis.text = element_text(size = 14), 
        axis.title = element_text(size = 16), 
        plot.title = element_text(size = 20), 
        plot.subtitle = element_text(size = 18, face = c("bold.italic")), 
        legend.text = element_text(size = 16),
        legend.box.just = "top",
        legend.box = "vertical") + 
  guides(shape = guide_legend(override.aes = list(color = "black")))
```



```{r }
outcomes_df %>% 
  left_join(
    wide_sample_size_df %>% 
      mutate(n_ipd_total = ifelse(anchored_yn == "Yes", n_ipd_total/2, n_ipd_total)) %>% 
      select(doi, n_itc, n_ipd_total), 
    by = c("doi", "n_itc")
  ) %>% 
  filter(adjustment == "adjusted") %>% 
  ggplot(aes(x = adjustment,
             y = effect_benefit,
             # shape = adjustment
             )) + 
  # geom_violin() +
  geom_boxplot(fill = "white", outlier.shape = NA, width = 0.5) +
  geom_point(aes(x = n_ipd_total, color = significant_char), size = 1, width = 0.05, alpha = 0.5) +
  geom_hline(aes(yintercept = effect_cutoff), linetype = "dashed", color = "black") +
  # geom_blank(aes(y = max_num_comparison * 1.1, x = 3), inherit.aes = FALSE, data = labelling_data) +
  # scale_color_manual(values = c("Yes" = "#cc0000", "No" = "#000000", "Unknown" = "#D9D9D9")) +
  facet_wrap( ~ contrast, scales = "free", ncol = 1) + 
  coord_flip() + 
  labs(title = "PAITC treatment effects point estimates", 
       subtitle = "Left side of vertical dashed line favors IPD treatment", 
       color = "5% significance level", 
       shape = "Adjustment",
         y = "Relative treatment effect estimate", 
       x = NULL) +
  theme(legend.position = "right",
        # text = element_text(size = 14),
        axis.text.y = element_blank(),
        # axis.text = element_text(size = 14), 
        # axis.title = element_text(size = 16), 
        # plot.title = element_text(size = 20), 
        plot.subtitle = element_text(face = c("bold.italic")), 
        # legend.text = element_text(size = 16),
        legend.box.just = "top",
        legend.box = "horizontal") + 
  guides(shape = guide_legend(override.aes = list(color = "black")))
```

```{r}
outcomes_df %>% 
  filter(adjustment == "adjusted") %>% 
  mutate(contrast = factor(contrast, 
                           levels = c("Difference", "Rates/ratio"), 
                           labels = c("Mesure de l'effet : différence absolue", 
                                      "Mesure de l'effet : rates/ratio"))) %>% 
  ggplot(aes(x = adjustment,
             y = effect_benefit,
             # shape = adjustment
             )) + 
  geom_boxplot(fill = "white", outlier.shape = NA, width = 0.5) +
  geom_jitter(aes(color = significant_char), size = 1, width = 0.05, alpha = 0.7) +
  geom_hline(aes(yintercept = effect_cutoff), linetype = "dashed", color = "black") +
  # geom_blank(aes(y = max_num_comparison * 1.1, x = 3), inherit.aes = FALSE, data = labelling_data) +
  # scale_color_manual(values = c("Yes" = "#cc0000", "No" = "#000000", "Unknown" = "#D9D9D9")) +
  facet_wrap( ~ contrast, scales = "free", ncol = 1) + 
  coord_flip() + 
  scale_color_discrete(labels = c("Non", "Inconnu", "Oui")) + 
  labs(title = "Estimation de l'effet de traitement, ajustée via PAITC", 
       subtitle = "Côté gauche de la ligne verticale en pointillée montre un \neffet en faveur du traitement avec données individuelles", 
       color = "Effet statistiquement \nsignificatif (alpha = 5%)", 
       y = "Effet de traitement relatif", 
       x = NULL) +
  theme(legend.position = "right",
        axis.text.y = element_blank(),
        plot.subtitle = element_text(face = c("bold.italic")), 
        legend.box.just = "top",
        legend.box = "horizontal") + 
  guides(shape = guide_legend(override.aes = list(color = "black")))
ggsave(filename = "boxplot_effet_fr.png")
```


```{r}
outcomes_df %>% 
  filter(adjustment == "adjusted") %>% 
  mutate(contrast = factor(contrast, 
                           levels = c("Difference", "Rates/ratio"), 
                           labels = c("Mesure de l'effet : différence absolue", 
                                      "Mesure de l'effet : rates/ratio"))) %>% 
  ggplot(aes(x = adjustment,
             y = effect_benefit,
             # shape = adjustment
             )) + 
  geom_boxplot(fill = "white", outlier.shape = NA, width = 0.5) +
  geom_jitter(aes(color = significant_char), size = 1, width = 0.05, alpha = 0.7) +
  geom_hline(aes(yintercept = effect_cutoff), linetype = "dashed", color = "black") +
  # geom_blank(aes(y = max_num_comparison * 1.1, x = 3), inherit.aes = FALSE, data = labelling_data) +
  # scale_color_manual(values = c("Yes" = "#cc0000", "No" = "#000000", "Unknown" = "#D9D9D9")) +
  facet_wrap( ~ contrast, scales = "free", ncol = 1) + 
  coord_flip() + 
  scale_color_discrete(labels = c("Non", "Inconnu", "Oui")) + 
  labs(title = "Estimation de l'effet de traitement, ajustée via PAITC", 
       subtitle = "Côté gauche de la ligne verticale en pointillée montre un \neffet en faveur du traitement avec données individuelles", 
       color = "Effet statistiquement \nsignificatif (alpha = 5%)", 
       y = "Effet de traitement relatif", 
       x = NULL) +
  theme(legend.position = "right",
        axis.text.y = element_blank(),
        plot.subtitle = element_text(face = c("bold.italic")), 
        legend.box.just = "top",
        legend.box = "horizontal") + 
  guides(shape = guide_legend(override.aes = list(color = "black")))
ggsave(filename = "boxplot_effet_fr.png")
```



```{r, fig.width=14, fig.height=16}
outcomes_plot <- outcomes_df %>% 
  # select(num_comparison, contrast, effect_cutoff, adjustment, effect) %>% 
  # Keeping only data with both unadjusted and adjusted effect
  pivot_wider(id_cols = c(num_comparison, contrast),
              names_from = adjustment,
              values_from = effect) %>%
  filter(!is.na(adjusted) & ! is.na(unadjusted)) %>%
  pivot_longer(cols = c("adjusted", "unadjusted"), names_to = "adjustment", values_to = "effect") %>% 
  left_join(outcomes_df[, c("num_comparison", "contrast", "adjustment", "significant_char", "effect_cutoff")], 
            by = c("num_comparison", "contrast", "adjustment")) %>% 
  ggplot() + 
  geom_point(aes(y = num_comparison,
             color = significant_char, 
             x = effect,
             shape = adjustment,
             group = adjustment), size = 3) + 
  geom_line(aes(y = num_comparison,
             x = effect,
             group = num_comparison), size = 0.5, color = "darkgrey", linetype = 1) +
  geom_vline(aes(xintercept = effect_cutoff), linetype = "dashed", color = "black") +
  scale_color_manual(values = c("Yes" = "#cc0000", "No" = "#000000", "Unknown" = "#D9D9D9")) + 
  facet_wrap(~ contrast, scales = "free") + 
  # facet_zoom(xlim = c(-2, 2)) +
  labs(title = "PAITC: distance between adjusted and not-adjusted treatment effects point estimates", 
       subtitle = "Vertical dashed lines represent absence of treatment effect difference",
       color = "5% significance level", 
       shape = "Adjustment",
       x = "Treatment effect point estimate", 
       y = NULL) +
  theme(legend.position = "bottom",
        axis.text.y = element_blank(),
        text = element_text(size = 14),
        axis.text = element_text(size = 14), 
        axis.title = element_text(size = 16), 
        plot.title = element_text(size = 20), 
        plot.subtitle = element_text(size = 18, face = c("bold.italic")), 
        legend.text = element_text(size = 16),
        legend.box.just = "top",
        legend.box = "vertical") + 
  guides(shape = guide_legend(override.aes = list(color = "black")))
outcomes_plot
```


```{r}
library("ggforce")
library("patchwork")
plot1 <-  outcomes_df %>% 
  # select(num_comparison, contrast, effect_cutoff, adjustment, effect) %>% 
  # Keeping only data with both unadjusted and adjusted effect
  pivot_wider(id_cols = c(num_comparison, contrast),
              names_from = adjustment,
              values_from = effect) %>%
  filter(!is.na(adjusted) & ! is.na(unadjusted), 
         contrast == "Rates: OR/RR/means ratio") %>%
  pivot_longer(cols = c("adjusted", "unadjusted"), names_to = "adjustment", values_to = "effect") %>% 
  left_join(outcomes_df[, c("num_comparison", "contrast", "adjustment", "significant_char", "effect_cutoff")], 
            by = c("num_comparison", "contrast", "adjustment")) %>% 
  ggplot() + 
   geom_point(aes(y = num_comparison,
                  color = significant_char, 
                  x = effect,
                  shape = adjustment,
                  group = adjustment), size = 3) + 
   geom_line(aes(y = num_comparison,
                 x = effect,
                 group = num_comparison), size = 0.5, color = "darkgrey", linetype = 1) +
   geom_vline(aes(xintercept = effect_cutoff), linetype = "dashed", color = "black") +
   scale_color_manual(values = c("Yes" = "#cc0000", "No" = "#000000", "Unknown" = "#D9D9D9")) +
   facet_zoom(xlim = c(0, 6)) +
   # facet_wrap(~ contrast, scales = "free") + 
   labs(title = "", 
        subtitle = "Rates: OR/RR/means ratio",
        color = "5% significance level", 
        shape = "Adjustment",
        x = "Treatment effect point estimate", 
        y = NULL) +
   theme(legend.position = "bottom",
         axis.text.y = element_blank(),
         text = element_text(size = 14),
         axis.text = element_text(size = 14), 
         axis.title = element_text(size = 16), 
         plot.title = element_text(size = 20), 
         plot.subtitle = element_text(size = 18, face = c("bold.italic")), 
         legend.text = element_text(size = 16),
         legend.box.just = "top",
         legend.box = "vertical") + 
   guides(shape = guide_legend(override.aes = list(color = "black")))  +
  theme(strip.background = element_rect(fill = "grey"))

plot2 <- outcomes_df %>% 
  # select(num_comparison, contrast, effect_cutoff, adjustment, effect) %>% 
  # Keeping only data with both unadjusted and adjusted effect
  pivot_wider(id_cols = c(num_comparison, contrast),
              names_from = adjustment,
              values_from = effect) %>%
  filter(!is.na(adjusted) & ! is.na(unadjusted), 
         contrast == "Means/medians difference") %>%
  pivot_longer(cols = c("adjusted", "unadjusted"), names_to = "adjustment", values_to = "effect") %>% 
  left_join(outcomes_df[, c("num_comparison", "contrast", "adjustment", "significant_char", "effect_cutoff")], 
            by = c("num_comparison", "contrast", "adjustment")) %>% 
  ggplot() + 
   geom_point(aes(y = num_comparison,
                  color = significant_char, 
                  x = effect,
                  shape = adjustment,
                  group = adjustment), size = 3) + 
   geom_line(aes(y = num_comparison,
                 x = effect,
                 group = num_comparison), size = 0.5, color = "darkgrey", linetype = 1) +
   geom_vline(aes(xintercept = effect_cutoff), linetype = "dashed", color = "black") +
   scale_color_manual(values = c("Yes" = "#cc0000", "No" = "#000000", "Unknown" = "#D9D9D9")) +
   facet_zoom(xlim = c(-3, 3)) +
   # facet_wrap(~ contrast, scales = "free") + 
   labs(title = "", 
        subtitle = "Means/medians difference",
        color = "5% significance level", 
        shape = "Adjustment",
        x = "Treatment effect point estimate", 
        y = NULL) +
   theme(legend.position = "bottom",
         axis.text.y = element_blank(),
         text = element_text(size = 14),
         axis.text = element_text(size = 14), 
         axis.title = element_text(size = 16), 
         plot.title = element_text(size = 20), 
         plot.subtitle = element_text(size = 18, face = c("bold.italic")), 
         legend.text = element_text(size = 16),
         legend.box.just = "top",
         legend.box = "vertical") + 
   guides(shape = guide_legend(override.aes = list(color = "black"))) +
  theme(strip.background = element_rect(fill = "grey"))
```


```{r, fig.height=14, fig.width=12}
plot1 + plot2
```


